Glasshouse experiment

### 2018-03-13 experiment_info.Rmd
species so far
s
ideas

@@

>>>>

A common trend in natural ecosystems is pollinator sharing (REF). Therefore, pollen from different species can arrive to the stigmas of other species. The real impact of pollen in a natural ecosystem is still unknown. Nonetheless, some advances has been done with recent works where heterospecific pollen effect is evaluated (REFS).

@@

For all the species, the day prior anthesis flowers were emasculated and then hand-pollinated next day with toothpicks with 3-4 gentle touches over the stigma surface.

Table of species:

**Solanaceae**

SOLY "Tommy Joe"
CAAN "California Wonder""
PEIN "Petunia integrifolia"
SOME "Solanum melongera"

**Brassicaceae**

Sinapis alba White mustard
Brassica oleracea var. capitata
Brassica rapa var. chinensis

**Convolvulaceae**

Ipomoea purpurea

Possible species to include:

Ipomoea aquatica

I. coccinea

Convolvulus sabatius

Sysimbrium spp

Raphanus spp

Eruca sativa
